---
title: "Progress Memo 2"
subtitle: |
  | Final Project 
  | Data Science 1 with R (STAT 301-1)
author: "Sarah Norman"
pagetitle: "PM1 Sarah Norman"
date: "November 19, 2024"

format:
  html:
    toc: true
    toc-depth: 4
    toc-location: left
    embed-resources: true
    link-external-newwindow: true

execute:
  warning: false

from: markdown+emoji
reference-location: margin
citation-location: margin

---
```{r}
#| label: reading data/loading packages
#| echo: false

library(tidyverse)
library(readr)
library(naniar)
library(skimr)
library(janitor)
library(knitr)
library(ggcorrplot)
library(here)

skincare_malaysia <- read_csv(here("data/skincare_survey_malaysia_2021.csv"))
skincare_malaysia_original <- read_csv(here("data/skincare_survey_malaysia_2021.csv"))
```

::: {.callout-tip icon=false}

## Github Repo Link

[Sarah's Repo Link](https://github.com/stat301-1-2024-fall/final-project-1-sarahdnor.git)

:::

:::{.callout-tip icon=false}

## Data Source

Link:

[Skincare and Technology Survey Among Malaysians](https://www.kaggle.com/datasets/nurunnz/skincare-survey-among-malaysian-2021?resource=download)

APA Citation:

Nurunnajwa, Harith Hakim, and Azri Hadif. (2022). Skincare and Technology Survey Among Malaysian [Data set]. Kaggle. https://doi.org/10.34740/KAGGLE/DSV/3371747

:::


## About the data:

The Skincare Survey in Malaysia 2021 CSV dataset was collected by Nurunnajwa, Harith Hakim, and Azri Hadif, all of whom were students at Universiti Teknologi Malaysia at the time of data collection. I accessed this data on 10/31/2024 from Kaggle. The Temporal Coverage Start Date (when data collection began) was 11/30/2021, and the Temporal Coverage End Date (when data collection ended) was 12/30/2022. The specific report referenced in this memo does not have a published date; however, it appears that viewers have been downloading the dataset since October 2007, and the overall report was last updated three years ago. As stated in the report, "the goal of this data collection is to know the skin problems among Malaysians and the suitability of AI Face Scanners to track skin issues as a quick fix."


## Why this data

Given my major in International Studies, I take every opportunity to explore different countries of interest. Being born in Malaysia, I started examining datasets on Malaysia. I found this particular dataset intriguing due to its unusual specificity. I also I recall cosmetic surgery being a common topic of conversation among my peers when I was in the Philippines attending an international school. I was also drawn to the dataset's mention of AI, given its current prominence. I find it even more intriguing given that the dataset is quite old, prior to the surge in AI usage. This could provide an opportunity to further explore how AI technology has evolved. There is also an opportunity to discuss the disparities in perceptions of skincare between Western and Asian countries. As a young woman, I resonate with the challenges surrounding appearance and am eager to understand more about its impact on Southeast Asian culture. Additionally, I appreciate the variety of variables in this dataset, which offer a chance to experiment with both numbers and strings, further developing my skills.

## Data quality & complexity check


```{r}
#| label: tbl-1
#| tbl-cap: "Summary of Data"
#| echo: false

skim_without_charts(skincare_malaysia)
```



As seen in @tbl-1 the dataset has a total of 31 variables with a variety of both character and numerical variable types (17 and 14, respectively). The observations for the dataset, however, can be considered quite small, with the dataset having only 76 observations. However, I personally appreciate this dataset's size because I feel it represents a more realistic sample size for a survey that might be conducted on campus.

```{r}
#| label: tbl-2
#| tbl-cap: "Count of Different Occupations Surveyed"
#| echo: false

skincare_malaysia|>
  count(Occupation) |> 
  knitr::kable()


```

```{r}
#| label: tbl-3
#| tbl-cap: "Distribution of Gender"
#| echo: false

skincare_malaysia|>
  count(Gender) |> 
  knitr::kable()

```


The vast majority of the sample are university students (with 60 of the 76 observations being from students) and females (with 58 of the observations being female and 18 being male) which can be seen in @tbl-2 and @tbl-3.

This may lend the dataset to bias, given that its purpose is to better understand skin problems/perceptions and the use of AI face scanners across the country.

```{r}
#| label: tbl-4
#| tbl-cap: "Distribution of 'Race'"
#| echo: false

skincare_malaysia|>
  distinct(Race) |>
  knitr::kable()
```

It is also important to note that there is more than just one distinct race/nationality represented in the data set, despite the study claiming to explore the perceptions of specifically Malaysians. The report also claims that the geospatial coverage of the survey is "worldwide". This conflicting information will be further explored in the misc section of this memo.

However, The data does not experience significant missingness issues, only encountering missing values for age and the question "Do share your skincare goals and motivation with us!"

```{r}
#| label: fig-1
#| echo: false

skincare_malaysia |>
  select("Age", "Do share your skincare goals and motivation with us!") |>
  gg_miss_var() +
  labs(
    title = "Distribution of Missing Values"
  )

```

The final comments question ("Do share your skincare goals and motivation with us!") has a total of 18 missing values, while the age variable has 1 missing value (not posing great issues for the dataset) as seen in @fig-1. Given that the final comments question has relatively significant missingness, it can be inferred that it was an optional question.

The data appears to be relatively tidy. However, the column titles do not following the snake_case naming convention. Column names include capital letters and spaces but are also quite lengthy. Name cleaning and rewriting of column names (a combination of both the clean_names() function from the janitor package and string functions) will likely need to be done for clarity and aesthetics.

## Potential data issues

The last column of this dataset, alongside the multiple-choice answer questions (e.g., "Which, if any, of the following statements applies to you?"), is part of what drew me to this dataset, as they pose new challenges that I have yet to face in the course. However, I have yet to work with cells containing multiple values. Additionally, the final column, given that it consists of unique strings (individual written responses), will be difficult to examine but will provide interesting insights about perceptions of skincare and individual motivations. Some cleaning will also have to be done regarding some variable names such as the variables present under the "races" column shown above- perhaps some of this data can be changed into a factor data type. The term "race" also needs to be established, or perhaps the column name should be changed for greater accuracy.

## Misc

There are some point of confusion in the dataset:

The description and written components of the data contain various grammatical errors and conflicting points. This may indicate that the text was translated and could lead to challenges during the EDA. Despite these issues, the text remains understandable but appears less professional and organized.

There seems to be conflicting information regarding the demographics of the study. For example, the dataset claims to have worldwide geospatial coverage but has proportionally few responses from respondents of different races/nationalities. Additionally, there is some confusion about which age groups are targeted for the study, as the description discusses general Malaysian culture but also emphasises women and teenagers. The survey also seems to have been conducted in a university setting based on occupational observations.

Although this poses some confusion, as long as these components are clarified in the EDA, I don't believe they will create issues during analysis, as the values in the dataset are relatively clear and can always be manipulated.

Upon initial review of the data, some interesting areas for exploration include distinguishing differences across gender (acknowledging that there are more females than males represented in the dataset). It will also be interesting to extract similarities within the responses for the final questions, "Which, if any, of the following statements applies to you?" and "Do share your skincare goals and motivation with us!", especially since the final question is open-ended. I think there are a handful of different relationships that can be mapped.

## Tidying Data

As mentioned previously, this dataset requires tidying prior to exploratory data analysis (EDA). However, upon further investigation, extensive cleaning was needed in addition to the creation of a codebook.


```{r}
#| label: tidying-data
#| echo: false

# Cleaning names

skincare_malaysia <- skincare_malaysia |>
clean_names() 
  
# Renaming variables
  
skincare_malaysia <- skincare_malaysia |>
  rename(
    product_choice_process = how_do_did_you_choose_your_products,
    cultural_identity = race,
   purchase_frequency = how_often_do_you_buy_skincare_products,
  skincare_spending = on_average_how_much_do_you_spend_on_skincare_products_each_month,
  perceptions_of_ingredients = which_of_the_following_types_of_ingredients_would_make_you_more_likely_to_buy_a_skin_care_product,
  skincare_importance = do_you_agree_that_skincare_is_important,
  use_of_samples = do_you_use_samples_before_buying_skincare_products,
  trying_new_skincare = how_willing_are_you_to_try_different_skin_care_products,
  where_purchased = where_do_you_purchase_your_skin_care_products,
  time_spent_finding_routine = i_wasting_to_much_time_to_find_out_skincare_and_routine_that_suits_my_skin,
  doubts_skincare_media = i_being_doubtful_about_the_information_shared_by_influencers_and_brand_promoted_content,
  understanding_of_products = i_feel_difficult_to_understand_the_list_of_ingredients_on_the_products,
 product_no_improvement = i_bought_expensive_product_but_doesnt_see_any_improvement_on_my_skin,
 unaware_ingredient_quality = i_unaware_of_which_ingredients_is_the_best_or_to_avoid_according_my_skin_type,
 experienced_allergies = i_experienced_allergies_after_use_a_new_skincare_products_eg_rashness_acne_purging_etc,
 desire_skincare_efficiency = i_want_to_reduce_time_to_find_which_routine_products_suits_with_my_skin,
 want_solutions = i_want_have_solutions_from_expert_in_effortless_and_cheap_way,
desire_for_routine = i_want_to_have_my_personalized_skincare_routine_that_suitable_with_my_current_products,
desire_know_more = i_want_to_gain_knowledge_of_skincare_regime_in_easy_and_understandable_way,
desire_better_lifestyle = i_want_to_adapt_a_healthy_lifestyle_for_a_glowing_and_healthy_skin,
perceptions_of_technology = do_you_think_that_technology_can_improve_your_skincare_routine,
heard_of_ai = do_you_have_heard_about_ai_artificial_intelligent,
perceptions_skin_scanning = after_you_know_about_ai_do_you_want_to_have_a_skin_scanning_app_that_can_customize_skincare_regime,
excitment_skincare_ai = do_you_feel_excited_to_use_this_skincare_application,
motivations = do_share_your_skincare_goals_and_motivation_with_us,
skin_type = which_if_any_of_the_following_statements_applies_to_you,
skincare_experience = have_you_ever_used_any_skin_care_products
  ) |>
  mutate(
    cultural_identity = as.factor(str_to_lower(cultural_identity)),
    cultural_identity = fct_collapse(cultural_identity,
      "bumiputra sabah" = c("bumiputra sabah", "bumiputra sabah (bajau)", "sabahan"),
      "arab" = c("arabian", "arab"),
      "malay" = "malay",
      "korean" = "korean",
      "chinese" = "chinese",
      "libya" = "libya",
      "indian" = "indian",
      "african" = "african",
      "javanesse" = "javanesse",
      "iban" = "iban",
      "nigerian" = "nigerian",
      "sudanese" = "sudanese"),
    occupation = as.factor(str_to_lower(occupation)),
    gender = as.factor(str_to_lower(gender)),
    purchase_frequency = as.factor(str_to_lower(purchase_frequency)),
    product_choice_process = str_to_lower(product_choice_process),
    skincare_spending = as.factor(skincare_spending),
    skincare_experience = as.factor(skincare_experience)
  )

# Change factor order

skincare_spending_levels <- c("Less than RM 20", "RM 20 - RM 50", "RM 50 - RM 100", "RM 100 - RM 150", "> RM 150")

age_levels <- c("NA", "15-20", "20-25", "25-30", "30-35", ">35")


skincare_malaysia <- skincare_malaysia |>
  mutate(
    skincare_spending = factor(skincare_spending, levels = skincare_spending_levels),
    age = factor(age, levels = age_levels)
  ) 

```

The following steps were taken to tidy the data:

All columns have been renamed to follow the snake_case naming convention and revised for clarity, as many of the variable titles were excessively long and contained grammatical errors. This required each column to be renamed individually. In addition to cleaning names, variables were converted to lowercase (except for binary yes or no values). The newly named cultural_identity, occupation, gender, purchase_frequency, skincare_spending, and skincare_experience columns were converted to factors for ease and clarity of analysis. The skincare_spending variable had its factor levels reordered chronologically to make the data analysis more intuitive. Cultural_identity was modified to ensure that respondents who provided the same value with slight variations, such as differences in capitalization or acronyms, were grouped under the same factor variable.

```{r}
#| label: tbl-5
#| echo: false
#| tbl-cap: "Variable Name Comparison"

# skincare_malaysia_sample <- skincare_malaysia|>
#   slice_head(n = 10)

# kable(skincare_malaysia_sample)

column_comparison <- tibble(
  "New Names" = names(skincare_malaysia),
  "Original Names" = names(skincare_malaysia_original)
)

kable(column_comparison)

```

@tbl-5 shows a side-by-side comparison of the newly created names and the dataset's original names, highlighting the now clearer and more concise names following correct naming conventions.

```{r}
#| label: tbl-6
#| echo: false
#| tbl-cap: "Skincare Malaysia Codebook"

# Creating codebook
skincare_malaysia_codebook <- tibble(
  "Column Name" = c(
    "timestamp", "gender", "age", "cultural_identity", "occupation",
    "skincare_importance", "skincare_experience", "skin_type", "perceptions_of_ingredients",
    "product_choice_process", "use_of_samples", "purchase_frequency", "trying_new_skincare",
    "where_purchased", "skincare_spending", "time_spent_finding_routine", "doubts_skincare_media",
    "understanding_of_products", "product_no_improvement", "unaware_ingredient_quality",
    "experienced_allergies", "desire_skincare_efficiency", "want_solutions", "desire_for_routine",
    "desire_know_more", "desire_better_lifestyle", "perceptions_of_technology", "heard_of_ai",
    "perceptions_skin_scanning", "excitement_skincare_ai", "motivations"
  ),
  "Description" = c(
    "The timestamp indicating when the survey was submitted by the respondent",
    "The gender of the respondent",
    "The age bracket of the respondent, grouped in 5-year intervals",
    "The cultural identity of the respondent",
    "The occupation of the respondent",
    "The respondent's ranking of skincare importance on a scale of 1–5 (1 being low, 5 being very important)",
    "Whether the respondent has experience using skincare products",
    "Skin characteristics that apply to the respondent (e.g., oily skin, dark spots, etc.)",
    "Ingredients that make the respondent more likely to purchase a skincare product",
    "Factors that influence the respondent’s product purchasing decisions",
    "Whether the respondent uses samples before purchasing skincare products",
    "How often the respondent purchases new skincare products, on a scale of very often, often, sometimes, rarely, or never",
    "The respondent's willingness to try new products on a scale of 1–5 (1 being low, 5 being very high)",
    "The places where respondents purchase their skincare products",
    "The average amount spent on skincare products monthly, in Malaysian Ringgit",
    "The time wasted finding a suitable skincare routine, rated on a scale of 1–5 (1 being low, 5 being very high)",
    "The respondent's doubt about information shared by influencers and brand-promoted content, rated on a scale of 1–5 (1 being low, 5 being very high)",
    "The difficulty in understanding the list of ingredients in skincare products, rated on a scale of 1–5 (1 being easy, 5 being very difficult)",
    "Applicability of the statement: 'I have bought expensive products but didn't see any improvement in my skin,' rated on a scale of 1–5 (1 being not applicable, 5 being very applicable)",
    "The respondent's knowledge of which ingredients to avoid for their skin type, rated on a scale of 1–5 (1 being highly aware, 5 being unaware)",
    "Frequency of experiencing allergies after using a new skincare product (e.g., rashes, acne, purging), rated on a scale of 1–5 (1 being never, 5 being very frequent)",
    "The desire to reduce the time spent finding a suitable skincare routine, rated on a scale of 1–5 (1 being none, 5 being very high)",
    "The desire to receive expert skincare solutions in an effortless and affordable way, rated on a scale of 1–5 (1 being none, 5 being very high)",
    "The desire for a personalized skincare routine that suits the respondent's current products, rated on a scale of 1–5 (1 being none, 5 being very high)",
    "The desire to gain more knowledge about skincare routines, rated on a scale of 1–5 (1 being none, 5 being very high)",
    "The desire to adopt a healthy lifestyle for glowing and healthy skin, rated on a scale of 1–5 (1 being none, 5 being very high)",
    "The respondent's belief that technology can improve their skincare routine, rated on a scale of 1–5 (1 being none, 5 being very high)",
    "Whether the respondent has heard of AI face scanning",
    "Whether the respondent is willing to use a skin scanning app that can customize skincare routines",
    "The respondent's excitement about using AI skincare applications, rated on a scale of 1–5 (1 being little, 5 being very high)",
    "The respondent's goals and motivations for improving their skincare"
  )
)

kable(skincare_malaysia_codebook)

```

The original dataset lacked a codebook, necessitating the creation of the codebook shown in @tbl-6. Concerns arose due to the absence of a description for the ranking scale. As a result, the values represented by 1 to 5 had to be inferred. This was achieved by examining the first variable with this numeric ranking, skincare_importance, and deducing that most individuals considered skincare to be important. Since 5 was more predominant than 1, it was determined that 5 indicated skincare was very important, while 1 indicated that skincare was not important. This pattern was then used to infer the rankings for the other variables. While not ideal, thorough analysis can still be conducted.


## Distribution of respondent characteristics

The following section will engage in a univariate analysis of respondent characteristics to provide greater insight into the sample. This analysis will include exploring the distributions of cultural identity, occupation, age and gender.


```{r}
#| label: fig-2
#| echo: false

distribution_of_cultural_identity <- skincare_malaysia |>
ggplot(aes(y = cultural_identity)) +
  geom_bar() +
  labs(
    title = "Distribution of Cultural Identity",
    x = "Count",
    y = "Cultural Identity"
  )

ggsave(
  filename = "../plots/distribution-of-cultural_identity.png",
  plot = distribution_of_cultural_identity,
)

print(distribution_of_cultural_identity)

```



The above analysis was conducted to gain a greater understanding of the cultural makeup of the respondents. The bar graph shows that there are 15 unique cultural identities. These distinct values were originally under the column titled "race." However, this column was renamed to "cultural identity" for greater accuracy.

This specific title was chosen because "race" was not applicable, as it incorrectly categorized the values. Similarly, "ethnicity" was not a suitable descriptor, as some terms, such as Bumiputra Sabah and Bajau, are regional or legal classifications in Malaysia rather than purely ethnic groups. Additionally, terms like Libya and African denote nationalities or continents, which are not ethnicities. As a result, this variable is titled cultural identity, which is broad but still captures the diversity of the sample.

From @fig-2, we can see that there is a significant number of Malaysians (both those who identified as Malay and Bumiputra Sabah). This makes sense, given that the survey was conducted in Malaysia. However, we can still observe that a significant portion of respondents are not Malaysian.

```{r}
#| label: fig-3
#| echo: false

distribution_of_cultural_identity_other <- skincare_malaysia |>
  mutate(cultural_identity = fct_collapse(cultural_identity,
      "arab" = c("arabian", "arab"),
      "Malaysian" = c("bumiputra sabah", "bumiputra sabah (bajau)", "sabahan","malay"),
      "korean" = "korean",
      "chinese" = "chinese",
      "libya" = "libya",
      "indian" = "indian",
      "african" = "african",
      "javanesse" = "javanesse",
      "iban" = "iban",
      "nigerian" = "nigerian",
      "sudanese" = "sudanese"),
       cultural_identity  = fct_lump_lowfreq(cultural_identity)) |>
  ggplot(aes(y = cultural_identity)) +
  geom_bar() +
  labs(
    title = "Distribution of Cultural Identity: Malaysian and Other",
    x = "Count",
    y = "Cultural Identity"
  )

ggsave(
  filename = "../plots/distribution_of_cultural_identity_other.png",
  plot = distribution_of_cultural_identity_other,
)

print(distribution_of_cultural_identity_other)

```

We can see the distribution of Malaysians to other cultural identities more clearly in @fig-3. In the above graph, Sabahans were included under Malaysians so that we can more clearly see the distribution of those who are Malaysian and those who are not.

A predominantly Malaysian sample implies that the data generally reflects Malaysian cultural norms, behaviors, and perceptions. Analysis may therefore prove valuable in the context of Malaysia.

However, the large proportion of Malaysians may also lead to skewed results that don't accurately reflect other groups with differing cultural identities, as their skincare behaviors, cultural norms, and perceptions may vary due to this attribute. The findings, therefore, may not capture the diversity of skincare behaviors and perceptions. This may limit the applicability of the findings to broader or different cultural groups.


```{r}
#| label: fig-4
#| echo: false

#distribution-of-occupation

distribution_of_occupation <- skincare_malaysia |>
  mutate(occupation = occupation |> fct_infreq() |> fct_rev()) |>
  ggplot(aes(x = occupation)) +
  geom_bar() +
  labs(
    title = "Distribution of Occupation",
    x = "Occupaton",
    y = "Count"
  )

ggsave(
  filename = "../plots/distribution_of_occupation.png",
  plot = distribution_of_occupation,
)

print(distribution_of_occupation)

```


@fig-4 displays the distribution of occupations among respondents. From the graph, we can see that the majority of respondents are students.

```{r}
#| label: fig-5
#| echo: false

distribution_of_occupation_other <- skincare_malaysia |>
  mutate(
    occupation = fct_lump_lowfreq(occupation),
    occupation = occupation |> fct_infreq() |> fct_rev()
    ) |>
  ggplot(aes(x = occupation)) +
  geom_bar() +
  labs(
    title = "Distribution of Occupation: Student and Other",
    x = "Occupation",
    y = "Count"
  )

print(distribution_of_occupation_other)
```
@fig-5 more clearly shows the distribution of students compared to those with other occupations, indicating that there are significantly more students than any other occupation. This makes sense given that the data was collected by students from Universiti Teknologi Malaysia. This once again highlights how findings may be limited to a specific demographic of Malaysians (Malaysian students) and may be less generalizable to individuals in other occupations.


```{r}
#| label: fig-6
#| echo: false

age_levels <- c("NA", "15-20", "20-25", "25-30", "30-35", ">35")

distribution_age <- skincare_malaysia |>
  mutate(
   age = factor(age, levels = age_levels)
  ) |>
  ggplot(aes(x = age)) +
  geom_bar() +
  labs(
    title = "Distribution of Respodent Age",
    x = "Age Bracket",
    y = "Count"
  )

print(distribution_age)
```

@fig-6 shows the distribution of age amongst respondents, broken up into 5-year age brackets. We can see that ages between 15 to 20 and 20 to 25 are the most prominent. This makes sense given that the vast majority of respondents are university students. However, it would have been useful to have the raw age of respondents, as there is a significant difference between individuals who are 15 and those who are 20, especially since the teenage years can be very formative, particularly with regard to puberty. This data supports previous analysis that the majority of respondents are younger students; however, given the large brackets for age, individual analysis of age may not be very informative.

```{r}
#| label: tbl-proportion-of-gender
#| echo: false

#proportion-of-gender

gender_proportion <- skincare_malaysia |>
    group_by(gender) |>
    summarise(count = n()) |>
    mutate(proportion = count / sum(count))

kable(gender_proportion, caption = "Proportion of Gender")
```
Finally, @tbl-proportion-of-gender displays the proportion of male to female respondents from the survey, showing that there were significantly more females than males who completed it.

From this distribution analysis, we can gain a better understanding of the demographic makeup in this dataset, allowing us to draw more accurate assumptions and conclusions.


## Data broken up by gender

The following section will focus on multivariate analysis to explore the disparities between female and male respondents. This analysis is driven by stereotypes about the attitudes of women and men regarding appearance, such as the belief that women care more about their appearance and that men are less hygienic. The purpose of this analysis is to test these stereotypes.

The below table displays the proportion of males and females that have experience using skincare.

```{r}
#| label: tbl-importance_by_gender
#| echo: false
#| tbl-cap: "Proportion of Females and Males with Skincare Experience"

gender_experience_skincare <- skincare_malaysia |>
  group_by(gender) |>
  summarise(
    prop_skincare_experience_yes = mean(skincare_experience == "Yes", na.rm = TRUE)
    )

kable(gender_experience_skincare)

```

The @tbl-importance_by_gender indicates that men have less experience using skincare compared to women. However, it is important to note that, as shown in @tbl-proportion-of-gender, fewer males are represented in the survey, which may make the results less accurate for this demographic.

```{r}
#| label: fig-7
#| echo: false

skincare_important_and_ingredient_knowledge <- skincare_malaysia |>
  ggplot(aes(x = unaware_ingredient_quality, y = skincare_importance, color = gender)) +
  geom_jitter() +
  labs(
    title = "Relationship Between Skincare Importance and Ingrediedent Knowledge and Gender",
    x = "Rating of Understanding of Skincare Ingredients",
    y = "Rating of Skincare Importance"
  )

ggsave(
  filename = "../plots/skincare_important_and_ingredient_knowledge.png",
  plot = skincare_important_and_ingredient_knowledge,
)

print(skincare_important_and_ingredient_knowledge)
```


@fig-7 shows no clear correlation between skincare value and ingredient understanding, as there is no strong linear relationship between these variables. However, the data points concentrate in the top half of the plot as understanding increases, suggesting a slight positive trend for both groups.

The plot challenges gender stereotypes, as both men and women show diverse attitudes across the full range of skincare importance ratings. The relationship between ingredient knowledge and importance also appears consistent across genders. 

Given that male respondents are distributed throughout the plot, including at high levels of both metrics, this plot contradicts assumptions about men being universally less interested in skincare.


```{r}
#| label: fig-8
#| echo: false

skincare_malaysia_spending <- skincare_malaysia |>
  mutate(
    skincare_spending = fct_recode(skincare_spending,
      "10" = "Less than RM 20",
      "35" = "RM 20 - RM 50",
      "75" = "RM 50 - RM 100",
      "125" = "RM 100 - RM 150",
      "175" = "> RM 150"
     ) 
  ) |>
  count(skincare_spending, gender) |>
  group_by(skincare_spending) |>
  mutate(
    percentage = n/sum(n)
  )

# skincare_malaysia_spending

skincare_malaysia_spending_plot <- skincare_malaysia_spending |>
  ggplot(aes(x = skincare_spending, y = percentage, fill = gender)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Proportion of Monthly Spending Brackets by Gender",
    y = "Percentage",
    x = "Monthly Skincare Spending in Malaysian Ringgit"
  )

ggsave(
  filename = "../plots/skincare_malaysia_spending_plot.png",
  plot = skincare_malaysia_spending_plot,
)

print(skincare_malaysia_spending_plot)
```

@fig-8 illustrates the monthly skincare spending in Malaysian Ringgit by gender. The data show that women account for a larger proportion of spenders across all categories, which is expected given that there are more females than males in the sample. However, the disparity between males and females becomes notably larger in the higher spending brackets. In other words, men's representation decreases as spending increases, comprising about 40% of the lowest spending category but only about 10% of the highest. This graph supports claims that men spend less on skincare than women. However, given that there is still a presence of men, the graph challenges the notion that men don't care about or invest in skincare at all.

## Correlation analysis

A skincare correlation matrix has been created to more clearly see the relationships between all numerical variables at once. By visualizing these relationships, patterns and trends can be identified, fostering a better understanding of how variables impact one another, fueling further exploration and guiding sections of this report.

```{r}
#| label: fig-9
#| echo: false

skincare_malaysia_means <- skincare_malaysia |>
  group_by(understanding_of_products) |>
  mutate(
      skincare_spending = fct_recode(skincare_spending,
          "Less than RM 20" = "10",
          "RM 20 – RM 50" = "35",
          "RM 50 – RM 100" = "75",
          "RM 100 – RM 150" = "125",
          "> RM 150" = "175",
)
  ) |>
  summarise(
    mean_skincare_spending = mean(as.numeric(skincare_spending), na.rm = TRUE),
    mean_skincare_importance = mean(skincare_importance, na.rm = TRUE),
    mean_new_skincare = mean(trying_new_skincare, na.rm = TRUE),
    mean_time_spent_finding_skincare = mean(time_spent_finding_routine, na.rm = TRUE),
    mean_doubts_skincare_media = mean(doubts_skincare_media, na.rm = TRUE),
    mean_product_improvement = mean(product_no_improvement, na.rm = TRUE),
    mean_unaware_ingredient_quality = mean(unaware_ingredient_quality, na.rm = TRUE),
    mean_allergy_experience = mean(experienced_allergies, na.rm = TRUE),
    mean_desired_skincare_efficiency = mean(desire_skincare_efficiency, na.rm = TRUE),
    mean_want_solutions = mean(want_solutions, na.rm = TRUE),
    mean_desire_rountine = mean(desire_for_routine, na.rm = TRUE),
    mean_desire_know_more = mean(desire_know_more, na.rm = TRUE),
    mean_desired_skincare_efficiency = mean(desire_skincare_efficiency, na.rm = TRUE),
    mean_want_solutions = mean(desire_better_lifestyle, na.rm = TRUE),
    mean_excitment_skincare_ai = mean(excitment_skincare_ai, na.rm = TRUE)
  )

#skincare_malaysia_means

skincare_malaysia_means_plots <- skincare_malaysia_means |>
  cor() |>
  ggcorrplot() +
  labs(
    title = "Correlation Matrix of Skincare Survey Variables"
  )

ggsave(
  filename = "../plots/skincare_malaysia_means_plots.png",
  plot = skincare_malaysia_means_plots,
)

print(skincare_malaysia_means_plots)
```


A lot of these correlations in @fig-9 are fairly intuitive. For example, mean_skincare_importance and mean_skincare_spending show a strong positive correlation, which makes sense as those who value skincare are likely to spend more to ensure they are getting the highest quality products and/or are constantly buying new products to try. Similarly, mean_allergy_experience positively correlates with mean_doubts_skincare_media. This suggests that individuals who have experienced allergy-related issues with skincare may be more likely to distrust media claims about products.

## Use of AI

This analysis utilized AI, specifically ChatGPT-4 and ChatGPT-3, for problem-solving, as well as for spelling and grammar checks. Text was frequently input into ChatGPT to review and correct spelling and grammar. On a few occasions, code was also input into ChatGPT for debugging; however, the platform did not prove to be particularly helpful in this regard, producing overly complicated solutions using unfamiliar functions and arguments.

## Summary of progress

I initially anticipated engaging in more coding for Memo 2, as I believed the data to be relatively clean. However, upon attempting to work with the data, I found that it was incredibly messy, particularly with the column names, and I noticed there was no codebook. This resulted in me doing a lot of additional work that I hadn't anticipated. Even after individually altering every column name, correcting various variables (in terms of syntax and datatype), and creating a codebook from scratch, I was still able to include good univariate analysis. As a result, I believe good progress was made on this memo, as my data is now usable, and I am very familiar with the variables (having read and renamed each one according to its original purpose). So far, I have completed univariate analysis of the sample and have begun analysis aimed at evaluating gender stereotypes around skincare, alongside creating a correlation matrix of the numerical variables.

## Next steps

I plan to undertake more complex data analysis, as my univariate analysis is relatively complete. This will involve more bivariate and multivariate exploration. I aim to dedicate a significant portion of this assignment to exploring the string variables skin_type and motivations, which consist of lists provided by respondents. For instance, I plan to extract specific skin types and potentially create dummy variables to indicate whether someone has, for example, oily skin or dark spots (potentially expanding the dataset). This could allow me to identify relationships between individual skin types and other factors, such as skincare concerns, cultural identities, or allergies.

Since the data did not come with an initial codebook, I will need to manually scan the dataset to identify the full range of possible answers for skin_type, which will be a time-consuming process. For the motivations column, I plan to use string functions to identify patterns and similarities in respondents' answers.

Additionally, I want to create a dedicated section in this report to analyze perceptions and use of AI in skincare. I also intend to spend more time examining the correlation matrix to uncover interesting findings and ensure these insights are presented in a way that feels relevant and important to the overall report.
